\thesistitle

### 2019-07-04 sections/research.tex
Type 3 shortcomings

\subsection{Type 3 clones}\label{sec:type3}
Type 3 clones are \textit{copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}. Detection of clones by this definition can be very hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed. Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold \cite{svajlenko2014evaluating, cordy2011nicad}. This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance) \cite{lavoie2011automated}, token-level similarity of statement-level similarity.

Having a definition that allows for any change in code poses serious challenges on refactoring. A levenshtein distance of one can already change the meaning of a code fragment significantly, for instance if the name of a type differs by a character (and thus referring to different types).

>>>>

\subsection{Type 3 clones}\label{sec:type3}
Type 3 clones are \textit{copied fragments with further modification (with added, removed or changed statements)}~\cite{roy2007survey}. Detection of clones by this definition can be hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed. Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold~\cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}. This similarity threshold has been implemented in different ways: textual similarity (for instance using Levenshtein distance)~\cite{lavoie2011automated}, token-level similarity~\cite{sajnani2016sourcerercc} or statement-level similarity~\cite{kamalpriya2017enhancing}.

Having a definition that allows for any change in code poses serious challenges on refactoring. A Levenshtein distance of one can already change the meaning of a code fragment significantly, for instance, if the name of a type differs by a character (and thus referring to different types).
